Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-12-15 ms.tex
mispelled alskeys middlename

\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}

>>>>

\author[Generozov, Stone, \& Metzger]{Aleksey S. Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}
